---
title: "The cranly package"
output: html_notebook
---


`cranly`, released to CRAN in March 2018 by Ioannis Kosmidis, is a very polished tool for exploring CRAN packages.

```{r}
library(cranly)
library(tidyverse)
```

Fetch the package data base from CRAN usint the `CRAN_padkage_db()` function in the `tools` package and save it to disk.

```{r,include=FALSE}
p_db_052518 <- tools::CRAN_package_db()
save(p_db_052518, file = "p_db_052518.RDA")
```   

Load the data base from disk and have a look at it.
```{r}
load(file = "p_db_052518.RDA")
class(p_db_052518)
glimpse(p_db_052518) 
```

Clean the data base using the built in function:
`clean_CRAN_db(packages_db = tools::CRAN_package_db(),
  clean_directives = clean_up_directives, clean_author = clean_up_author)`. 

```{r}
package_db <- clean_CRAN_db(p_db_052518)

```

Note that there is quite a bit of hard-coded stuff in the clean function.

```{r}
#clean_up_author
``` 

### Look at Package Networks

```{r,message=FALSE,warning=FALSE}
package_network <- build_network(package_db)
package_summaries <- summary(package_network)
plot(package_summaries, according_to = "n_imported_by", top = 20)
```

Here is the Page Rank for the top 20.
```{r}
plot(package_summaries, according_to = "page_rank", top = 20)
```

### Collaboration Networks
Set up to plot packages by authors.

```{r}
author_network <- build_network(object = package_db, perspective = "author")
```

#### Jeff Ryan
```{r}
plot(author_network, author = "Jeffrey A Ryan", exact = FALSE)
```

#### Dirk Eddelbuettel
```{r}
plot(author_network, author = "Dirk Eddelbuettel", exact = FALSE)
```


### Create Package Dependency Tree   


```{r}
xts_tree <- build_dependence_tree(package_network, "xts")
plot(xts_tree)
```   



### Search for Packages

```{r}
Bayesian_packages <- package_with(package_network, name = c("Bayes", "MCMC"))
plot(package_network, package = Bayesian_packages, legend=FALSE)

```




